---
title: "SL Assignment 1"
author: "Pamela Afful"
format: 
    pdf:
      fig-pos: 'H'
editor: visual
---

```{r libs, eval=TRUE, echo=FALSE}
#| message: false
#| warning: false

# install.packages(c("modelsummary", "fixest"))

#install.packages("GGally")
#install.packages("gtsummary")
#install.packages('stargazer')
#install.packages('patchwork')
#install.packages("glmnet")
#install.packages('lmridge')
#install.packages('MASS')

library(dplyr)
library(knitr)
#library(skimr)
library(plotly)
library(ggplot2)
library(ggpubr)
library(lubridate)
library(zoo)
library(tidyverse)
library(GGally)
library(modelsummary)
library(stargazer)
library(gtsummary)
library(patchwork)
library(glmnet)
library(lmridge)
library(tidyr)
library(caret)
library(MASS)
library(dplyr)
```

```{r, data_read,echo=FALSE,eval=TRUE}
boston_data_training=read.csv('my_boston.csv')
boston_data=read.csv("boston.csv")

#View(boston_data)
```

# Exploratory Data Analysis

```{r, dtypes,echo=FALSE,eval=TRUE}
#| echo: false




kable(data.frame(row_count=nrow(boston_data) , column_count=ncol(boston_data)),
      caption = "boston data attributes")


```

```{r,na_count_per_col,echo=FALSE,eval=TRUE}

col_types = sapply(boston_data, class)

col_types_df = data.frame(column = names(col_types), DataType = as.character(col_types))

#kable(col_types_df,caption = "boston data column data types")

col=c('column','na_count')
na_cnt=data.frame(colSums(is.na(boston_data))) %>%
  rownames_to_column("old_index") %>% 
  rename_with(~ col)




kable(left_join(col_types_df,na_cnt,by='column'),caption='Boston Data Column Attributes')


```

```{r target_val_dist, eval=TRUE, echo=FALSE}

boston_data %>% dplyr::select(all_of(names(boston_data))) %>% mutate(chas=factor(chas,levels=c(0,1))) %>% 
  ggplot(aes(x=medv) ) +
  geom_boxplot() +
  labs(title = "distribution of median house values",x='median house value')+
  theme_minimal()



```

```{r feat_corr, eval=TRUE, echo=FALSE}
#| message: false
#| warning: false
#| fig-height: 12
#| fig-width: 14

# comeback and make this look better
# feat=c("crim",    "zn"      "indus"   "chas"    "nox"     "rm"      "age"     "dis"     "rad"     "tax"     "ptratio" "lstat"   "medv" )

boston_data %>% dplyr::select(all_of(names(boston_data))) %>% mutate(chas=factor(chas,levels=c(0,1))) %>% 
  ggpairs(columns=1:13,mapping = aes(color = chas) ) +
  labs(title = "Feature Pairwise Plot")+
  theme_minimal()
```

```{r,corr}
library(reshape2)
corr_data=boston_data %>% mutate(chas=factor(chas)) %>% 
  dplyr::select(where(is.numeric)) %>% 
  cor(use = "pairwise.complete.obs")


corr_data_df=melt(corr_data)

corr_data_df %>% ggplot(aes(x=Var2, y=Var1, fill=value))+
geom_tile() +
  scale_fill_gradient2(low = "blue", high = "red", mid = "white", 
                       midpoint = 0, limit = c(-1,1), space = "Lab", 
                       name="Pearson\nCorrelation") +
  geom_text(aes(label = round(value, 2)), color = "black")+
  labs(title = "Feature Correlation Matrix",x='Feature',y='Feature')+
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5, hjust = 1))


  
```

# Model Building

```{r,lm_fit,eval=TRUE, echo=FALSE}

#| message: false
#| warning: false

# Scale the data before training
features=head(names(boston_data_training),-1)
boston_data_training=as.tibble(boston_data_training) 

# Scale the data- standardization
# Every feaure except the chas feature
scaled_trd=data.frame(scale(boston_data_training %>% dplyr::select(any_of(features[features!='chas']))))

scaled_trd$chas=boston_data_training$chas
scaled_trd$medv=boston_data_training$medv

tr_d=boston_data_training %>% 
    mutate(chas=factor(chas,levels=c(0,1))) 



all_feat_model=lm(medv ~ ., data=tr_d)
summary(all_feat_model)
  
# modelsummary(
#   all_feat_model,
#   stars = TRUE,
#   title = "Regression Results- All Features",
#   output = "latex" 
# )


# all_feat_model %>%
#   tbl_regression() %>%  
# add_glance_source_note() %>%
#   add_global_p()
```

Model Performance

-   The model shows a relatively good fit to the training data, with \~73% of the variation in the data, captured/explained by the model

-   10 out of 12 (check again) are significant at the 5% level

-   Comeback\*

**Prediction of test dataset**

```{r,test_pred,eval=TRUE,echo=FALSE}


row_labels_training = rownames(boston_data_training)
row_labels_all=rownames(boston_data)

test_indicies=setdiff(row_labels_all,row_labels_training)
test_data=boston_data %>% slice(sapply(test_indicies,as.integer))
a=colnames(test_data)
features=a[1:length(a)-1]
new_data=test_data %>% dplyr::select(all_of(features)) %>% mutate(chas=factor(chas,levels=c(0,1)))

scaled_test_features=data.frame(scale(new_data %>% 
        dplyr::select(any_of(features[!features %in% c('chas','zn')])
               )) )
scaled_test_features$chas=new_data$chas
scaled_test_features$zn=new_data$zn
#scaled_test_features$medv=test_data$medv

      
test_predictions=predict(all_feat_model,newdata=new_data)



```

```{r,test_mse,eval=TRUE,echo=FALSE}

y_true=test_data$medv
mse_func=function(ytrue,y_pred){
  errors=y_true-y_pred
  mse=mean(errors**2)
  return(mse)
}

mse_base=mse_func(y_true,test_predictions)

aic_base=AIC(all_feat_model,k=2) # use default value
bic_base=BIC(all_feat_model)


mse_func(y_true,test_predictions)
bic_base
```

# Model Improvement

**Backwards Step wise Variable Selection**

ref website:<https://alain-vandormael.netlify.app/post/varselect/#:~:text=Stepwise%20regression,next%20deletion%20increases%20the%20AIC.>

```{r,bk_step,echo=FALSE,eval=TRUE}

# Backwides Stepwise Regression
# incrementally decrease the number of features from the regression 
# For each removal, fit the model
# apply fit model on test data-subsetted for the selected features
# store the mse for each iteration

mses=c()
model_feat=c()
aics=c()
bics=c()

set.seed(123)

# MANUAL FOR LOOP

for(i in 1:length(features)-1  ){
  new_features=head(features,-i)
  model_feat=c(model_feat,length(new_features))
  train_set=boston_data_training %>% mutate(chas=factor(chas,levels=c(0,1)))%>% dplyr::select( all_of( c('medv',new_features)))
  sel_feat_model=lm(medv ~ ., data=train_set)
  new_data_i=test_data %>% mutate(chas=factor(chas,levels=c(0,1))) %>%
    dplyr::select(all_of(new_features)) 
  train_predictions_i=predict(sel_feat_model)#newdata=new_data_i use training vals
  y_true=train_set %>% dplyr::select(medv) %>% pull()
  error_i=mse_func(y_true,train_predictions_i)
  mses=c(mses,error_i)
  aic=AIC(sel_feat_model,k=2) # using default value
  bic=AIC(sel_feat_model)
  aics=c(aics,aic)
  bics=c(bics,bic)
}

mod0=lm(medv ~1 , data=tr_d) 
bk_model=step(all_feat_model,direction='backward',scope=formula(mod0), trace = 0)

# Using in-built packages
# Mass Package
# Implemetation
# Using with CV
# Using AIC and the discriminating metric
# lower bound- intercept regression
# train_set = trainControl(method="cv", number=10) # cv
# cv_mod_feat_sel = train(medv ~ ., data=tr_d,  scope = formula(mod0),method="lmStepAIC", direction="backward", trace=FALSE, trControl=train_set,preProcess='scale') #use CV to train using CV using the stepAIC method
# 
# cv_mod_feat_sel$finalModel;AIC(cv_mod_feat_sel$finalModel)
# 
# bk_feat_model=stepAIC(all_feat_model, direction = "backward", scope = formula(mod0), trace=FALSE) # bk selection model
# 
# 
#bk_feat_model$anova

# coef(bk_feat_model) # 10/13 coefficients/features elected from bk elimination
# AIC(bk_feat_model) # best AIC score 
# bk_feat_model$anova







```

```{r,plot_bk_metrics,echo=FALSE,eval=F}

mses[1]=mse_base
model_feat[1]=12 # replace with baseline model number of features
aics[1]=aic_base


 # replace with baseline model number of features
bics[1]=bic_base

# Create dataframe from the above
backwards_feat_sel_metrics=data.frame(number_features=model_feat,aic=aics,bic=bics,mse=mses)
aic_plot=backwards_feat_sel_metrics %>% 
  mutate(number_features=factor(number_features)) %>% 
  ggplot(aes(x=number_features,y=aic,group = 1,color='blue'))+
  geom_line()+
  geom_point()+
  labs(title = "Training AIC vs Number of Training Features- Backward Stepwise Selection",x='#Features',y='train AIC')+
  geom_vline(xintercept = 12) +
  annotate("text", x = 10.5, y = 2800, label = "Baseline-all features", angle = 0)+
  theme_minimal()

bic_plot=backwards_feat_sel_metrics %>% 
  mutate(number_features=factor(number_features)) %>% 
  ggplot(aes(x=number_features,y=bic,group = 1,color='blue'))+
  geom_line()+
  geom_point()+
  labs(title = "Training BIC vs Number of Training Features- Backward Stepwise Selection",x='#Features',y='train BIC')+
  geom_vline(xintercept = 12) +
  annotate("text", x = 10.5, y = 2800, label = "Baseline-all features", angle = 0)+
  theme_minimal()

mse_plot=backwards_feat_sel_metrics %>% 
  mutate(number_features=factor(number_features)) %>% 
  ggplot(aes(x=number_features,y=mse,group = 1,color='blue'))+
  geom_line()+
  geom_point()+
  labs(title = "Training MSE vs Number of Training Features- Backward Stepwise Selection",x='#Features',y='train MSE')+
  geom_vline(xintercept = 12) +
  annotate("text", x = 10.5, y = 40, label = "Baseline-all features", angle = 0)+
  theme_minimal()


aic_plot/bic_plot/mse_plot
```

```{r,ridge_regr,eval=TRUE,echo=FALSE}

regressors= boston_data_training %>% mutate(chas=factor(chas,levels=c(0,1)))%>% dplyr::select( all_of( c('medv',features)))
regressors_x=model.matrix(medv~.,data=regressors)[,-1]
y=boston_data_training$medv

# use lmridge , fit for a range of alphas
# from the lm ride documentation, the regressors are scaled, the "scale" option scales the data st it has mean=0 and var=1
# Using this method so we can track the aic
# Use various values of K/alpha and use AIC/BIC to choose the best penalty parameter 
ridge_model =lmridge(y~., data = boston_data_training, K = seq(0, 0.1, 0.01) , scaling = "scaled")


# get predictions
#ridge_pred=predict(ridge_model,newdata=test_data)

# get ridge metrics
#mse_ridge=mse_func(y_true,ridge_pred)
#mse_ridge

# get AIC
info_criteria=infocr(ridge_model)
info_criteria_df=as.data.frame(info_criteria)

info_criteria_df$K=seq(0, 0.1, 0.01) 

pivot_longer(info_criteria_df,
                    cols=c('AIC','BIC'),
                    names_to='IC Metric',
                    values_to='Score'
                    ) %>% 
  ggplot(aes(x=K,y=Score,color=`IC Metric`))+
  geom_line()+
  geom_point()+
  labs(title = "Ridge Regression Training AIC/BIC",x='alpha',y='Score')+
  theme_minimal()
  

```

Best lambda val=0 for AIC consideration

```{r,ridge_regr,eval=TRUE,echo=FALSE}
x=data.matrix(boston_data_training[, features])
y=boston_data_training$medv
cv_model_ridge=cv.glmnet(x, y, alpha = 0) # using kfolds, k=10

#plot(cv_model)

coef(cv_model_ridge, s = "lambda.1se")

```

```{r,lasso_regr,eval=TRUE,echo=FALSE}
x=data.matrix(boston_data_training[, features])
y=boston_data_training$medv
cv_model_lasso=cv.glmnet(x, y, alpha = 1) # using kfolds, k=10

#plot(cv_model) 
# Top numbers= no. of non zero coefficients for that value of lambda
# 
coef(cv_model_lasso, s = "lambda.1se") # best trade off between model simplicity and accurancy
```

```{r pred_mse, eval=TRUE, echo=F}
#| message: false
#| warning: false

test_data_feat=test_data %>% mutate(chas=factor(chas,levels=c(0,1)))%>% 
  dplyr::select(all_of(features))

test_data_feat_x=data.matrix(test_data[, features])
y_test_true=as.vector(test_data %>% dplyr::select(medv) %>% pull())


bk_test_predictions=predict(bk_model,newdata=test_data_feat)
bk_test_predictions=as.vector(bk_test_predictions)
lasso_test_predictions=as.vector(unname(predict(cv_model_lasso,newx=test_data_feat_x)))
ridge_test_predictions=as.vector(unname(predict(cv_model_ridge,newx=test_data_feat_x)))

all_test_predictions=data.frame(backward_selection=bk_test_predictions,
                           ridge_predictions=ridge_test_predictions,
                           lasso_predictions=lasso_test_predictions,
                           y_true=y_test_true,
                           pred_id=1:106
                           )

test_mses=c(mse_base)


for(pred in head(names(all_test_predictions),-1) ){
  model_pred=all_test_predictions %>% dplyr::select(any_of(pred)) %>% pull()
  test_mse_i=mse_func(y_test_true,model_pred)
  test_mses=c(test_mses,test_mse_i)
  
}
  
test_mses # add plot of ytrue vs predictions from the 

all_test_predictions %>% ggplot(aes(x=pred_id)) + 
  geom_line(aes(y = y_true, color = "ytrue"))+
  geom_line(aes(y = backward_selection, color = "Backward Selection y_hat"))+
  geom_line(aes(y = ridge_predictions, color = "Ridge y_hat"))+
  geom_line(aes(y = ridge_predictions, color = "Lasso y_hat"))+
  labs(title = "Test Data Prediction Comparison",x='observation index',y='y')+
  theme_minimal()

  
test_mses_df=data.frame(metric=c('MSE'),all_features=test_mses[1],backwise_step=test_mses[2]                             ,ridge=test_mses[3],lasso=test_mses[3]
                        )

rownames(test_mses_df) <- test_mses_df$MSE
kable(test_mses_df,caption = 'Model MSE Metrics')
```

\*best model= all features model (yikes!)

```{r, interaction,eval=TRUE,echo=F}



```
