---
title: "Supervised Learning Assignment 1"
author: "Pamela Afful"
format: 
    pdf:
      fig-pos: 'H'

editor: visual
titlepage: "UCTLogo.jpg"

execute: 
  cache: false
  warning: false
  message: false
  echo: false
---

```{r libs, eval=TRUE, echo=FALSE}
#| message: false
#| warning: false

# install.packages(c("modelsummary", "fixest"))

#install.packages("GGally")
#install.packages("gtsummary")
#install.packages('stargazer')
#install.packages('patchwork')
#install.packages("glmnet")
#install.packages('lmridge')
#install.packages('MASS')
#install.packages("interactions")
library(dplyr)
library(knitr)
#library(skimr)
library(plotly)
library(ggplot2)
library(ggpubr)
library(lubridate)
library(zoo)
library(tidyverse)
library(GGally)
library(modelsummary)
library(stargazer)
library(gtsummary)
library(patchwork)
library(glmnet)
library(lmridge)
library(tidyr)
library(caret)
library(MASS)
library(dplyr)
library(interactions)
library(kableExtra)
library(patchwork) 
```

```{r, data_read,echo=FALSE,eval=TRUE}
boston_data_training=read.csv('my_boston.csv')
boston_data=read.csv("boston.csv")


```

# Introduction

This reporrt analyses and models median house proces across a range of features inlcluding taxes, property and crime rates. The median house value is regressed against these features using several regression models, namely staight linear regression using all features, backwise step regression, ridge regression and lasso regression. The out of sample mean sqaured errrs are assesed across the the results of these models. The inclusion of an interaction variables, chas_rm, is added to the best performing model\*

# Exploratory Data Analysis

For the sake of data and analysis completeness, EDA is conducted on the entire boston dataset.

**Data Attributes**

```{r data_atrr, eval=TRUE, echo=FALSE}
#| message: false
#| warning: false


kable(data.frame(row_count=nrow(boston_data) , column_count=ncol(boston_data)),
      caption = "boston data attributes")


```

```{r var_summary, eval=T, echo=F}
#| message: false
#| warning: false

col_types = sapply(boston_data, class)

col_types_df = data.frame(column = names(col_types), datatype = as.character(col_types))

#kable(col_types_df,caption = "boston data column data types")

col=c('column','na_count')
na_cnt=data.frame(colSums(is.na(boston_data))) %>%
  rownames_to_column("old_index") %>% 
  rename_with(~ col)


col_types=left_join(col_types_df,na_cnt,by='column') %>% rename(feature='column')

feat_mins=unname(sapply(boston_data,min))
feat_q1=sapply(boston_data, quantile, probs = 0.25, na.rm = TRUE)
feat_mean=sapply(boston_data, mean)
feat_median=sapply(boston_data, quantile, probs = 0.50, na.rm = TRUE)
feat_q75=sapply(boston_data, quantile, probs = 0.75, na.rm = TRUE)
feat_max=sapply(boston_data,max)
feat_var=sapply(boston_data,var)

variable_summ=data.frame(feature=names(boston_data), 
                         `min`=unname(sapply(boston_data,min)),
                         q25=unname(feat_q1),
                         `mean`=unname(feat_mean),
                         `meadian`=unname(feat_median),
                         q75=unname(feat_q75),
                          `max`=unname(feat_max),
                         `sd`=round(unname(feat_var),2)**0.5
                         
                         )

variable_summ=left_join(variable_summ,col_types,by='feature')

kable(variable_summ,caption='Boston Data Data Summary') %>% kable_styling(latex_options = "scale_down")

```

The complete data set contains 506 observations across 13 columns. The data is complete, with no null values, and all columns are registered as numeric. **Tax (28404), age (792), and zn (543)** display the greatest variance across the features, whilst **nox (0.01) and rm (0.49)** show the least variance across their respective values.

```{r feat_var,eval=FALSE,echo=F}
variable_summ %>% arrange(variance) %>%
  dplyr::select(feature,variance)
```

**Median House Value Distributions**

```{r target_val_dist, eval=TRUE, echo=FALSE}
#| message: false
#| warning: false
#| label: fig-medv_hist
#| fig-cap: "Median House Value Distribution"

boston_data %>% dplyr::select(all_of(names(boston_data))) %>% mutate(chas=factor(chas,levels=c(0,1))) %>% 
  ggplot(aes(x=medv) ) +
  geom_histogram(fill='steelblue') +
  labs(title = "Distribution of median house values",x='median house value')+
  theme_minimal()




```

```{r chas_dist, eval=TRUE, echo=FALSE}
#| message: false
#| warning: false
#| label: fig-chas_obs
#| fig-cap: "Observation Count Chas Factor"

boston_data %>% group_by(chas) %>% 
 summarize(row_cnt=length(medv)) %>% 
  mutate(chas=factor(chas,levels=c(0,1))) %>% 
    ggplot(aes(x=chas,y=row_cnt,group=1) ) +
  geom_col(fill = "steelblue") +
  labs(title = "count of observations by chas factor variable",x='chas',y='#observations')+
  theme_minimal()
```

The data data is imbalanced, with more observations for the chas class=0.

```{r medv, eval=TRUE, echo=FALSE}
#| message: false
#| warning: false
#| label: fig-chas_box
#| fig-cap: "Median House Value Distribution,Grouped by Chas"

ggplotly(boston_data %>%
  mutate(chas=factor(chas,levels=c(0,1))) %>% 
    ggplot(aes(x=chas,y=medv,fill = chas) ) +
  geom_boxplot() +
  labs(title = "Distribution of Median House Value Grouped By Chas",x='chas',y='median value')+
  theme_minimal())


```

The median house value for observations with chas=0 is slightly higher at 23.3K, and the observations in this group skew towards higher values, in contrast to the distribution of the chas=1 observations, which is relatively more balanced around the median. Despite the difference in distributions, the two box plots show some overlap, which could indicate that the difference in means of these two groups may not be statistically significant.

```{r rad_index_dist, eval=TRUE, echo=FALSE}
#| message: false
#| warning: false
#| label: fig-radial_index_obs
#| fig-cap: "Observation Count Per Radial Accessibility Index"


boston_data %>%
  mutate(rad=factor(rad,levels=(sort(unique(boston_data$rad)) ))) %>% 
  group_by(rad) %>% 
  summarize(row_cnt=length(medv)) %>% 
  ggplot(aes(x=rad,y=row_cnt) ) +
  geom_col(fill ='steelblue') +
  labs(title = "Distribution of Median House Value Grouped By Rad Index",x='rad index',y='#observations')+
  theme_minimal()
```

Most observations are contained with the rad values= 4,5 and 24

```{r,med_val_index,echo=FALSE,eval=TRUE}

#| label: fig-radial_index_box_plot
#| fig-cap: "Distribution of Median House Values by Radial Accesibility Index"

boston_data %>%
  mutate(rad=factor(rad,levels=(sort(unique(boston_data$rad)) ))) %>% 
  ggplot(aes(x=rad,y=medv,fill = rad) ) +
  geom_boxplot() +
  labs(title = "Distribution of Median House Value Grouped By Rad Index",x='rad index',y='median value')+
  theme_minimal()
  

```

Grouping house value distributions by the RAD index value shows that median house values do not consistently increase or decrease with changes in the rad index. Observations with a rad value of 24 display the lowest house values among the index groups.

**Feature Correlations**

```{r,eval=TRUE, echo=FALSE}

#| label: fig-heatmap
#| fig-cap: "Feature Correlations"

library(reshape2)
corr_data=boston_data %>% mutate(chas=factor(chas)) %>% 
  dplyr::select(where(is.numeric)) %>% 
  cor(use = "pairwise.complete.obs")


corr_data_df=melt(corr_data)

corr_data_df %>% ggplot(aes(x=Var2, y=Var1, fill=value))+
geom_tile() +
  scale_fill_gradient2(low = "blue", high = "red", mid = "white", 
                       midpoint = 0, limit = c(-1,1), space = "Lab", 
                       name="Pearson\nCorrelation") +
  geom_text(aes(label = round(value, 2)), color = "black")+
  labs(title = "Feature Correlation Matrix",x='Feature',y='Feature')+
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5, hjust = 1))


```

Features, **rm and lstat** display the largest correlation, in absolute value, with medv. the rad and tax variables are most most highly correlated variables amongst features- signaling a strong possibility of multicollinearity \*this could what is causing our variance to blow up-talk about the implications

```{r, eval=TRUE, echo=FALSE}
#| message: false
#| warning: false
#| label: fig-pairplot
#| fig-cap: "Feature Pairplot"
#| fig-height: 12
#| fig-width: 15

# comeback and make this look better
# feat=c("crim",    "zn"      "indus"   "chas"    "nox"     "rm"      "age"     "dis"     "rad"     "tax"     "ptratio" "lstat"   "medv" )

boston_data %>% dplyr::select(all_of(names(boston_data))) %>% mutate(chas=factor(chas,levels=c(0,1))) %>% 
  ggpairs(columns=1:13,mapping = aes(color = chas) ) +
  labs(title = "Feature Pairwise Plot")+
  theme_minimal()+
  theme(legend.position = "right")
```

Analyzing the significance of the the correlations, the correlations between the response variable, medv, and all the other numeric features look to be significant at 5%.

# Model Building

```{r lm_fit, eval=TRUE, echo=FALSE}
#| message: false
#| warning: false

# Scale the data before training
features=head(names(boston_data_training),-1)
boston_data_training=as.tibble(boston_data_training) 

# Scale the data- standardization
# Every feaure except the chas feature
scaled_trd=data.frame(scale(boston_data_training %>% dplyr::select(any_of(features[features!='chas']))))


tr_d=boston_data_training %>% 
    mutate(chas=factor(chas,levels=c(0,1))) 



all_feat_model=lm(medv ~ ., data=tr_d)


stargazer(all_feat_model, 
          type='text', 
          digits = 2, 
          title = 'Baseline Model:All Feature Regression Summary', 
          style = 'qje')

```

Model Performance:

-   The model shows a relatively good fit to the training data, with \~74% of the variation in the data, explained by the model

-   10 out of the 12 feature coefficients (excluding the intercept) are statistically different from 0 at at lest the 10% level, with 9 of these significant at the 1% level

-   Nitrogen Oxide (nox) levelsshow the biggest marginal change , in absolute value, to median house values, medv, with an estimated negative change of -20.6K in estimated average houspe values per one unit increase in nox levels.

-   The F statistic is also significant at the 1% level, indicating that the coefficients of the model are jointly statistically different from 0.

**Prediction of test data set**

```{r,test_pred,eval=TRUE,echo=FALSE}


row_labels_training = rownames(boston_data_training)
row_labels_all=rownames(boston_data)

test_indicies=setdiff(row_labels_all,row_labels_training)
test_data=boston_data %>% slice(sapply(test_indicies,as.integer))
a=colnames(test_data)
features=a[1:length(a)-1]
new_data=test_data %>% dplyr::select(all_of(features)) %>% mutate(chas=factor(chas,levels=c(0,1)))

scaled_test_features=data.frame(scale(new_data %>% 
        dplyr::select(any_of(features[!features %in% c('chas','zn')])
               )) )
scaled_test_features$chas=new_data$chas
scaled_test_features$zn=new_data$zn
#scaled_test_features$medv=test_data$medv

      
test_predictions=predict(all_feat_model,newdata=new_data)



```

```{r,test_mse,eval=TRUE,echo=FALSE}

mse_func=function(ytrue,y_pred){
  errors=ytrue-y_pred
  mse=mean(errors**2)
  return(mse)
}

y_true=test_data$medv

mse_base=mse_func(y_true,test_predictions)

aic_base=AIC(all_feat_model,k=2) # use default value
bic_base=BIC(all_feat_model)


bl_mse=data.frame(`baseline mse`=round(mse_func(y_true,test_predictions),2))
kable(bl_mse,caption='Baseline Test MSE')

```

The out-of-sample (OOO) MSE for the baseline model is at 16.64K, that is, on average the baseline model's home values predictions are expected to deviate from the actual by this value, which is greater that the standard deviation of median house values of \~9.2.

# Model Improvement

**Backwards Step wise Variable Selection**

Method:

1.  Start off with the baseline model: regress response variable against all features
2.  Iteratively remove one feature, retrain the model and store both the AIC and BIC scores for each retrained model.

ref website:<https://alain-vandormael.netlify.app/post/varselect/#:~:text=Stepwise%20regression,next%20deletion%20increases%20the%20AIC.>

```{r,bk_step,echo=FALSE,eval=TRUE}

#| label: fig-barplot
#| fig-cap: "AIC and BIC curves per Backwise Steo Regression Iteration"

# Backwides Stepwise Regression
# incrementally decrease the number of features from the regression 
# For each removal, fit the model
# apply fit model on test data-subsetted for the selected features
# store the mse for each iteration

mses=c()
model_feat=c()
aics=c()
bics=c()

set.seed(718)

# MANUAL FOR LOOP

for(i in 1:length(features)-1  ){
  new_features=head(features,-i)
  model_feat=c(model_feat,length(new_features))
  train_set=boston_data_training %>% mutate(chas=factor(chas,levels=c(0,1)))%>% dplyr::select( all_of( c('medv',new_features)))
  sel_feat_model=lm(medv ~ ., data=train_set)
  new_data_i=test_data %>% mutate(chas=factor(chas,levels=c(0,1))) %>%
    dplyr::select(all_of(new_features)) 
  train_predictions_i=predict(sel_feat_model)#newdata=new_data_i use training vals
  y_true=train_set %>% dplyr::select(medv) %>% pull()
  error_i=mse_func(y_true,train_predictions_i)
  mses=c(mses,error_i)
  aic=AIC(sel_feat_model,k=2) # using default value
  bic=AIC(sel_feat_model)
  aics=c(aics,aic)
  bics=c(bics,bic)
}

models = list()
mod0=lm(medv ~1 , data=tr_d) 
bk_model=stepAIC(all_feat_model,direction='backward',scope=formula(mod0), trace =0,keep=function(model, AIC) {
    models[[length(models) + 1]] <<- model # keep/store all intermediate models as well as their AIC scores
    return(AIC) }
    )



# Store into a dataframe

results <- data.frame(
  Step = seq_along(models),
  AIC = sapply(models, AIC),
  BIC = sapply(models, BIC),
  Variables = sapply(models, function(m) {
    paste(names(coef(m))[-1], collapse = ", ")
  })
)

p=results %>% mutate(Step=factor(Step,levels=c(1,2,3))) %>% 
  ggplot(aes(x = Step,group=1)) +
  geom_line(aes(y = AIC, color = "AIC")) +
  geom_point(aes(y = AIC, color = "AIC")) +
  geom_line(aes(y = BIC, color = "BIC")) +
  geom_point(aes(y = BIC, color = "BIC")) +
  scale_color_manual(
    name = "Metric",
    values = c("AIC" = "red", "BIC" = "blue")
  ) +
  labs(
    title = "AIC and BIC Scores per Backward Regression Iteration",
    x = "Iteration Step",
    y = "IC Score"
  ) +
  theme_minimal()

ggplotly(p)

```

```{r bk_summ, eval=TRUE, echo=FALSE}
#| message: false
#| warning: false

stargazer(bk_model, 
          type='text', 
          digits = 2, 
          title = 'Backwise Step Best Model Regression Summary ', 
          style = 'qje')

```

Backward Step Regression Results:

1.  The step model reached the lowest AIC (\~2408) and BIC(\~2456) after 3 iterations with 10 out of the 12 features retained.

2.  Retained Features: **crime, zn, chas, nox, rm, dis, rad, tax, ptratio and lstat** with the **age** and **indus** variables removed**.** All of these are still statistically significant at least up to the 10% level.

3.  All regressors also maintain their sign with very little changes to their maginal effects with respect to the response variable.

4.  R square (\~74%) and the F statistic (significant at 1%) are still comparable and in the same region as the baseline model

```{r,plot_bk_metrics,echo=FALSE,eval=F}

mses[1]=mse_base
model_feat[1]=12 # replace with baseline model number of features
aics[1]=aic_base


 # replace with baseline model number of features
bics[1]=bic_base

# Create dataframe from the above
backwards_feat_sel_metrics=data.frame(number_features=model_feat,aic=aics,bic=bics,mse=mses)
aic_plot=backwards_feat_sel_metrics %>% 
  mutate(number_features=factor(number_features)) %>% 
  ggplot(aes(x=number_features,y=aic,group = 1,color='blue'))+
  geom_line()+
  geom_point()+
  labs(title = "Training AIC vs Number of Training Features- Backward Stepwise Selection",x='#Features',y='train AIC')+
  geom_vline(xintercept = 12) +
  annotate("text", x = 10.5, y = 2800, label = "Baseline-all features", angle = 0)+
  theme_minimal()

bic_plot=backwards_feat_sel_metrics %>% 
  mutate(number_features=factor(number_features)) %>% 
  ggplot(aes(x=number_features,y=bic,group = 1,color='blue'))+
  geom_line()+
  geom_point()+
  labs(title = "Training BIC vs Number of Training Features- Backward Stepwise Selection",x='#Features',y='train BIC')+
  geom_vline(xintercept = 12) +
  annotate("text", x = 10.5, y = 2800, label = "Baseline-all features", angle = 0)+
  theme_minimal()

mse_plot=backwards_feat_sel_metrics %>% 
  mutate(number_features=factor(number_features)) %>% 
  ggplot(aes(x=number_features,y=mse,group = 1,color='blue'))+
  geom_line()+
  geom_point()+
  labs(title = "Training MSE vs Number of Training Features- Backward Stepwise Selection",x='#Features',y='train MSE')+
  geom_vline(xintercept = 12) +
  annotate("text", x = 10.5, y = 40, label = "Baseline-all features", angle = 0)+
  theme_minimal()


aic_plot/bic_plot/mse_plot
```

**Ridge Regression**

```{r,ridge_regr,eval=TRUE,echo=FALSE}

regressors= boston_data_training %>% mutate(chas=factor(chas,levels=c(0,1)))%>% dplyr::select( all_of( c('medv',features)))
regressors_x=model.matrix(medv~.,data=regressors)[,-1]
y=boston_data_training$medv

# use lmridge , fit for a range of alphas
# from the lm ride documentation, the regressors are scaled, the "scale" option scales the data st it has mean=0 and var=1
# Using this method so we can track the aic
# Use various values of K/alpha and use AIC/BIC to choose the best penalty parameter 
ridge_model =lmridge(y~., data = boston_data_training, K = seq(0, 0.1, 0.01) , scaling = "scaled")


# get predictions
#ridge_pred=predict(ridge_model,newdata=test_data)

# get ridge metrics
#mse_ridge=mse_func(y_true,ridge_pred)
#mse_ridge

# get AIC
info_criteria=infocr(ridge_model)
info_criteria_df=as.data.frame(info_criteria)

info_criteria_df$K=seq(0, 0.1, 0.01) 

pivot_longer(info_criteria_df,
                    cols=c('AIC','BIC'),
                    names_to='IC Metric',
                    values_to='Score'
                    ) %>% 
  ggplot(aes(x=K,y=Score,color=`IC Metric`))+
  geom_line()+
  geom_point()+
  labs(title = "Ridge Regression Training AIC/BIC",x='alpha',y='Score')+
  theme_minimal()
  

```

Best lambda val=0 for AIC consideration

```{r,ridge_regr_coeff,eval=TRUE,echo=FALSE}
x=data.matrix(boston_data_training[, features])
y=boston_data_training$medv
cv_model_ridge=cv.glmnet(x, y, alpha = 0) # using kfolds, k=10

#plot(cv_model)

coef(cv_model_ridge, s = "lambda.1se")

```

```{r,lasso_regr,eval=TRUE,echo=FALSE}
x=data.matrix(boston_data_training[, features])
y=boston_data_training$medv
cv_model_lasso=cv.glmnet(x, y, alpha = 1) # using kfolds, k=10

#plot(cv_model) 
# Top numbers= no. of non zero coefficients for that value of lambda
# 
coef(cv_model_lasso, s = "lambda.1se") # best trade off between model simplicity and accurancy
```

```{r pred_mse, eval=TRUE, echo=F}
#| message: false
#| warning: false

test_data_feat=test_data %>% mutate(chas=factor(chas,levels=c(0,1)))%>% 
  dplyr::select(all_of(features))

test_data_feat_x=data.matrix(test_data[, features])
y_test_true=as.vector(test_data %>% dplyr::select(medv) %>% pull())


bk_test_predictions=predict(bk_model,newdata=test_data_feat)
bk_test_predictions=as.vector(bk_test_predictions)
lasso_test_predictions=as.vector(unname(predict(cv_model_lasso,newx=test_data_feat_x)))
ridge_test_predictions=as.vector(unname(predict(cv_model_ridge,newx=test_data_feat_x)))

all_test_predictions=data.frame(backward_selection=bk_test_predictions,
                           ridge_predictions=ridge_test_predictions,
                           lasso_predictions=lasso_test_predictions,
                           y_true=y_test_true,
                           pred_id=1:106
                           )

test_mses=c(mse_base)


for(pred in head(names(all_test_predictions),-1) ){
  model_pred=all_test_predictions %>% dplyr::select(any_of(pred)) %>% pull()
  test_mse_i=mse_func(y_test_true,model_pred)
  test_mses=c(test_mses,test_mse_i)
  
}
  
test_mses # add plot of ytrue vs predictions from the 

all_test_predictions %>% ggplot(aes(x=pred_id)) + 
  geom_line(aes(y = y_true, color = "ytrue"))+
  geom_line(aes(y = backward_selection, color = "Backward Selection y_hat"))+
  geom_line(aes(y = ridge_predictions, color = "Ridge y_hat"))+
  geom_line(aes(y = ridge_predictions, color = "Lasso y_hat"))+
  labs(title = "Test Data Prediction Comparison",x='observation index',y='y')+
  theme_minimal()

  
test_mses_df=data.frame(metric=c('MSE'),all_features=test_mses[1],backwise_step=test_mses[2]                             ,ridge=test_mses[3],lasso=test_mses[3]
                        )

rownames(test_mses_df) <- test_mses_df$MSE
kable(test_mses_df,caption = 'Model MSE Metrics')
```

\*best model= all features model (yikes!)

<https://statisticsbyjim.com/regression/interaction-effects/>

```{r, interaction,eval=F,echo=F}

# find an article to support this

# cantidates= indus*dis or indus*nox (high population traffic area- more polution)

# use an interaction plot to spot possible interactions

#features
# boston_data$chas=factor(boston_data$chas,levels=c(0,1))
# with(boston_data,{interaction.plot(chas,rad,medv,fixed=T)}
# )

vars=names(all_feat_model$coefficients)
vars_final=vars[vars!='chas1']
 

coeff=numeric()

for(i in 1:length(all_feat_model$coefficients)){
 coeff[i]= all_feat_model$coefficients[[i]]
}


vars[i]

chas_ind=which(vars=='chas1')
chas_coeff=coeff[chas_ind]
chas_= boston_data_training %>% dplyr::select(chas) %>% pull()
coeff=coeff[-chas_ind]

# features[features!='chas']
# c_=all_feat_model$coefficients
# c_[!c_ %in% c('chas')]



for(i in 2:length(vars_final)){
  var_name=vars_final[i]
  #i=2
  x_df =boston_data_training %>%
  dplyr::select(any_of(c(var_name, 'chas', 'medv') )) 
  x=x_df %>% dplyr::select(var_name) %>% pull()
  f_x=function(x) coeff[1]+coeff[i]*x+chas_coeff*chas_
  x_df$predictions=f_x(x)
  
  p <- ggplot(x_df, aes(x = .data[[var_name]], color = factor(chas))) +
    geom_point(aes(y = medv)) +
    geom_line(aes(y = predictions, group = chas)) +
    labs(
      title = paste("Response vs", var_name),
      x = var_name,
      y = "medv"
    ) +
    theme_minimal()
  
  print(ggplotly(p))
    
  
  
  
  
}
# Roupgly the difference between the two groups shoulf form a straight line which we could interprete as either an interaction exists or not


```

```{r int_corrs}
#| message: false
#| warning: false
#| fig-height: 12
#| fig-width: 14
# iteratively add interactition variables
# Create them with chas

int_feats=c('medv')
for(i in features){
boston_data=boston_data %>% mutate(!!paste0(i, "_chas") := .data[[i]] * chas)

int_feats=c(int_feats,paste0(i, "_chas"))
 
}



# Look at which interactions have strongest correlation with medv

corr_data=boston_data %>% mutate(chas=factor(chas)) %>% 
  dplyr::select(any_of(int_feats)) %>% 
  cor(use = "pairwise.complete.obs")


# corr_data_df=melt(corr_data)
# 
# corr_data_df %>% ggplot(aes(x=Var2, y=Var1, fill=value))+
# geom_tile() +
#   scale_fill_gradient2(low = "blue", high = "red", mid = "white", 
#                        midpoint = 0, limit = c(-1,1), space = "Lab", 
#                        name="Pearson\nCorrelation") +
#   geom_text(aes(label = round(value, 2)), color = "black")+
#   labs(title = "Feature Correlation Matrix",x='Feature',y='Feature')+
#   theme(axis.text.x = element_text(angle = 45, vjust = 0.5, hjust = 1))

boston_data %>% dplyr::select(any_of(int_feats)) %>% 
  ggpairs(columns=1:length(int_feats)) +
  labs(title = " and Feature Pairwise Plot")+
  theme_minimal()

```

Median House Values, medv, shows the highest correlation with the rm_chas interaction variable. Look at and this correlation also happens to be statistically significant at 5%.

```{r,int_regress}

# best performing regression =all_feat regression

int_training_data= boston_data_training %>% mutate(rm_chas=chas*rm)
int_features=features
int_features[length(int_features)+1]='rm_chas'
int_tr_d=int_training_data %>% dplyr::select( any_of(c(int_features,'medv')))

all_feat_with_int_model=lm(medv ~ ., data=int_tr_d)
summary(all_feat_with_int_model)



```

rm_chas did not turn out to be significant- but I'm not sure if this is as a result of the data imbalance (lot more chas=0 than 1) ?

```{r,int_mse,echo=F,eval=T}
int_test_data=test_data
int_test_data$rm_chas=int_test_data$chas*int_test_data$rm
int_test_d=int_test_data %>% dplyr::select(any_of(c(features,'rm_chas')))

int_test_pred=predict(all_feat_with_int_model,newdata=int_test_d)
```

```{r,int_mse_2, echo=FALSE,eval=T}

mse_func(int_test_data$medv,int_test_pred);16.6422	# oos mse improves, although the addition of the int variable is not significant?

```

# Residual Diagnostics

```{r,train_errors_hist,echo=F,eval=T}
errors=resid(all_feat_model)
test_err=test_data$medv-test_predictions
hist(errors,main='Distribution of Train Errors')
hist(test_err,main='Distribution of Test Errors')


```

```{r,errors_qq,echo=F,eval=T}

plot(all_feat_model, which = 2) # definately not normal 

```

```{r,err_homo,eval=T,echo=F}
plot(all_feat_model, which = 3) # NOT HOMOSCEDASTIC!!!

```
